Comparing heatmap functions in R

### 2019-08-10 analysis/paper/preliminary/comparing-heatmaps.Rmd
added Rmd file for comparing heatmap functions in R

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "August 3, 2019"
bibliography: research.bib
linkReferences: true
link-citations: true 
output: 
  bookdown::html_document2: 
    code_folding: hide
    self_contained: no
    keep_md: true
  bookdown::pdf_document2:
    fig_caption: true
    keep_tex: true
---

```{r child = "abstract.Rmd", eval = TRUE}
```

```{r child="intro.Rmd", eval = TRUE}
```

@@

`r if (eval_code) knitr::knit(text = out[[2]])`

`r if (eval_code) knitr::knit(text = out[[3]])`

`r if (eval_code) knitr::knit(text = out[[4]])`

`r if (eval_code) knitr::knit(text = out[[5]])`

```{r read_results, child = "results.Rmd", eval = TRUE}
```

```{r read_discussion, child = "discussion.Rmd", eval = TRUE}
```

# Colophon

This report was generated on ` r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE, echo = TRUE, tidy.opts=list(width.cutoff=50), size = "tiny", results = "markup"}
# which R packages and versions?
devtools::session_info()
```

The current Git commit details are:

```{r git2r, cache = FALSE, echo = TRUE}
# what commit is this file at?
git2r::repository(here::here())
```

>>>>

---
title: "Comparing heatmap functions in R"
author: "Frederick Boehm"
date: "8/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The goal here is to compare heatmaps that are produced by R functions. I'm particularly excited by interactive heatmaps, like those using D3 javascript.

@@

### `iheatmapr` R package

I installed the `iheatmapr` package from Github: `ropensci/iheatmapr`.
